---
title: "Biomass Estimation from raw FIA data."
author: "Sean DuBois"
date: "June 3, 2016"
output: html_document
---

## SQL Queries most recent survey

Query SQL for FIA Survey data, and select the cycle and subcycle closest to the specified year. Select FIA Tree and Plot data, and return a csv with this data.
Note on running code: Code from each section will be run only if the output from the code is not found in the data directory.

Note on querying PostgreSQL: SQL is queried with user name 'postgres' within the database 'postgres.' A password is not needed with a valid pgpass.conf file.

```{r Survey_data}
library(knitr)
library(dplyr)
library(plyr)
library(raster)

if ('full_fia_long.csv' %in% list.files('data/output/')) {
  surv.current <- read.csv('data/output/full_fia_long.csv', header = TRUE)
} else {
  if ('state_mat.csv' %in% list.files('data/output/')) {
  state.mat <- read.csv('data/output/state_mat.csv', header = TRUE)
  source('R_scripts/SQL_Query4.R')
  } else {source('R_scripts/Query_Survey.R')
    source('R_scripts/SQL_Query4.R')
  }
}

```

## Estimate Jenkins Biomass
Use the method from Jenkins et al. 2004 to estimate tree level biomass from the FIA tree data:

```{r Jenkins_biomass}

source('R_scripts/Jenkins_biom.R')

tree_data <- jenkins_biom(surv.current, write_out = TRUE)

```

## Estimate FIA Biomass

Use the FIA biomass estimates to get tree level biomass:

```{r FIA_biomass}

source('R_scripts/FIA_biom.R')

tree_data <- fia_biom(tree_data, write_out = TRUE)

```

## Estimate PEcAn Biomass
Use the PEcAn allometry package to calculate tree level biomass from the FIA tree data
```{r PEcAn_biomass}

source('R_scripts/PEcAn_biom.R')

tree_data <- pecan_biom(tree_data, write_out = TRUE)

```

## Aggregate Biomass

Aggregate Jenkins, FIA, and PEcAn biomass estimtates to the plot level. Returns csv of all three biomass estimates at the plot level, by species

```{r Aggregate_biomass}

source('R_scripts/Plot_biom_agg.R')

jenk_plots <- agg_to_plot(tree_data, "biomass_jenk")
fia_plots <-  agg_to_plot(tree_data,  "biomass_fia")
pecan_pred <- agg_to_plot(tree_data,  "biomass_pecan_pred_mean")
pecan_conf <- agg_to_plot(tree_data,  "biomass_pecan_conf_mean")

```

## Estimate Forest Parameters
Create estimates for mean DBH, density, and basal area and aggregate to the plot level. Returns a csv with these estimates at the plot level, by species.

```{r Aggregate_parameters}

source('R_scripts/Plot_parameters_agg.R')

```

## Rasterize Biomass

Create rasters containing 8km x 8km estimates for each biomass method, by species.
Note: requires table of location data, containing latitude and longitude for each FIA plot used. This table needs to be found in ```print(data/plt_location/plt_cn_values.csv)```

```{r Rasterize_Biomass}
source('R_scripts/Rasterize_biom.R')
```

## Rasterize Forest Parameters

Create rasters containing 8km x 8km estimates for DBH, density, and basal area, by species.
Note: requires table of location data, containing latitude and longitude for each FIA plot used. This table needs to be found in ```print(data/plt_location/plt_cn_values.csv)```
```{r Rasterize_Parameters}
source('R_scripts/Rasterize_parameters.R')
```
