---
title: "Control"
author: "Sean"
date: "June 3, 2016"
output: html_document
---

## Select most recent survey
Query SQL for FIA Survey data, and select the cycle and subcycle closest to the specified year 
```{r Survey_data}
library(knitr)
source('~/PalEON-FIA/Query_Survey.R')
```

## Select FIA data from SQL
Select FIA Tree and Plot data, and return a csv with this data
```{r Tree_data}
source('~/PalEON-FIA/SQL_Query4.R')
```

## Estimate Jenkins Biomass
Use the method from Jenkins et al. 2004 to estimate tree level biomass from the FIA tree data
```{r Jenkins_biomass}
source('~/PalEON-FIA/Jenkins_biom.R')
```

## Estimate FIA Biomass
Use the FIA biomass estimates to get tree level biomass
```{r FIA_biomass}
source('~/PalEON-FIA/FIA_biom.R')
```

## Estimate PEcAn Biomass
Use the PEcAn allometry package to calculate tree level biomass from the FIA tree data
```{r PEcAn_biomass}
source('~/PalEON-FIA/PEcAn_biom.R')
```

## Aggregate Biomass
Aggregate Jenkins, FIA, and PEcAn biomass estimtates to the plot level. Returns csv of all three biomass estimates at the plot level, by species
```{r Aggregate_biomass}
source('~/PalEON-FIA/Plot_biom_agg.R')
```

## Rasterize Biomass
Create rasters containing 8km x 8km estimates for each biomass method, by species
```{r Aggregate_biomass}
source('~/PalEON-FIA/Rasterize_biom.R')
```
