---
title: "Control"
author: "Sean"
date: "June 3, 2016"
output: html_document
---

## SQL Queries most recent survey
Query SQL for FIA Survey data, and select the cycle and subcycle closest to the specified year. Select FIA Tree and Plot data, and return a csv with this data.
Note on running code: Code from each section will be run only if the output from the code is not found in the data directory
Note on querying PostgreSQL: SQL is queried with user name 'postgres' within the database 'postgres.' A password is not needed with a valid pgpass.conf file.
```{r Survey_data}
library(knitr)
if ('full_fia_long.csv' %in% list.files('data/output/')){
  surv.current <- read.csv('data/output/full_fia_long.csv', header=TRUE)
} else {
  if('state_mat.csv' %in% list.files('data/output/')){
  state.mat <- read.csv('data/output/state_mat.csv', header=TRUE)
  source('R_scripts/SQL_Query4.R')
  } else {source('R_scripts/Query_Survey.R')
    source('R_scripts/SQL_Query4.R')
  }
}

```

## Estimate Jenkins Biomass
Use the method from Jenkins et al. 2004 to estimate tree level biomass from the FIA tree data
```{r Jenkins_biomass}
source('R_scripts/Jenkins_biom.R')
```

## Estimate FIA Biomass
Use the FIA biomass estimates to get tree level biomass
```{r FIA_biomass}
source('R_scripts/FIA_biom.R')
```

## Estimate PEcAn Biomass
Use the PEcAn allometry package to calculate tree level biomass from the FIA tree data
```{r PEcAn_biomass}
source('R_scripts/PEcAn_biom.R')
```

## Aggregate Biomass
Aggregate Jenkins, FIA, and PEcAn biomass estimtates to the plot level. Returns csv of all three biomass estimates at the plot level, by species
```{r Aggregate_biomass}
source('R_scripts/Plot_biom_agg.R')
```

## Rasterize Biomass
Create rasters containing 8km x 8km estimates for each biomass method, by species.
Note: requires table of location data, containing latitude and longitude for each FIA plot used. This table needs to be found in ```print(data/plt_location/plt_cn_values.csv)```
```{r Rasterize}
source('R_scripts/Rasterize_biom.R')
```
